systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2006-10-02 paper/trunk/systemfit_abstract.tex
changes according to the first major comment of reviewer A: modified title and a few sentences (package to estimate -> package for estimating; equation system -> system of equations)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@691 591db2bd-e0a0-4d22-8c19-2192dbb7da31
added instrumental variables as suggested by reviewer A.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@701 591db2bd-e0a0-4d22-8c19-2192dbb7da31
added examples of stat. analyses that use IV methods
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@702 591db2bd-e0a0-4d22-8c19-2192dbb7da3

\Abstract{
Many statistical analyses are based on models containing systems of
structurally related equations.
In cases where cross-equation disturbances are correlated,
full information methods are required \citep{zellner62}.
If exogenous variables are stochastically dependent
on the disturbances in the system,
then instrumental variable estimation methods should be used
\citep{zellner62b}
The package \pkg{systemfit} provides the capability
to estimate systems of linear equations
within the \proglang{R} programming environment.
}

\Keywords{R, simultaneous equations systems,
  seemingly unrelated regression, two-stage least squares,
  three-stage least squares}

>>>>

\Abstract{
Many statistical analyses (econometrics, biostatistics and
experimental design) are based on models containing systems of
structurally related equations.
In cases where cross-equation disturbances are correlated,
full information methods are required \citep{zellner62}.
If exogenous variables are stochastically dependent
on the disturbances in the system,
then instrumental variable estimation methods should be used
\citep{zellner62b}
The package \pkg{systemfit} provides the capability
to estimate systems of linear equations
within the \proglang{R} programming environment.
}

\Keywords{R, system of simultaneous equations,
  seemingly unrelated regression, two-stage least squares,
  three-stage least squares, instrumental variables}
